### 2019-09-23 uiuc.tex
updates about illinois section

Champaign-Urbana (CU), or colloquially known as Chambana, is home to the flagship campus of the University of Illinois system, the University of Illinois at Urbana-Champaign (UIUC). Since its foundations in the mid 19th century, it has flourished into the cultural hub of the midwest that it is today. CU houses many landmarks and districts, and it showcases both community and nationwide events annually. It is home to the Historic Virginia Theater, host to Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert. The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year. Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illinois Marathon.

CU is an industrial base to several major companies. This encompasses offices for Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm. Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, Jimmy John's, and high technology employer Wolfram Research. Carle has notably been affiliated with the creation of the first college in CU in over 60 years, the Carle Illinois College of Medicine -  ``the world's first engineering-based college of medicine". Research Park at the University of Illinois serves as a technology hub for several research and development ventures, where there are more than 120 companies employing 2,100 students and professionals in high-technology careers. Over 70 startup companies work in commercializing technology in Research Park.

@@

\subsubsection{Accommodations}
Information about facility/hotel space/capacity goes here - reference UNLV 2012, UPenn 2014, UW 2016

>>>>

Champaign-Urbana (CU), known colloquially as Chambana, is home to the state's flagship campus the University of Illinois at Urbana-Champaign (UIUC). Since its founding in the mid 19th century, it has grown into the flourishing cultural hub of the midwest that it is today. CU houses many landmarks and districts and showcases both local and national events annually. It is home to the Historic Virginia Theater, host of Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert. The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year. Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illini Marathon.

CU is an industrial base to several major companies including Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm. Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, and Wolfram Research. Carle has notably been affiliated with the creation of the first college in CU in over 60 years, the Carle Illinois College of Medicine -  ``the world's first engineering-based college of medicine". Research Park at the University of Illinois serves as a technology hub for several research and development ventures, where there are more than 120 companies employing 2,100 students and professionals in high-technology careers.

Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants. UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years. During this time researchers at UIUC made contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more. Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts. We hope to continue the nuclear tradition by hosting the ANS Student Conference in 2021.

@@
